---
title: "Financial Time Series"
author: "Faizan Khalid Mohsin"
date: "November 20, 2019"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



The subject is to analyse and model the dynamic  in the evolution of credit spread on S&P 500 high yield corporate bond market.

•	Introduction, (Already done)
•	Data, statistics (mean, kurtosiss, skewness, so on) and Differents tests ( Normality, Autocorrélation structuire, cointegration analysis, asymmetric analysis, so on) ( I have started but Not finish). Please change the variable credit spread. I have just done the difference but in the article the did difference but in continue time ( You will see) how they compute the credit spread. Et after rerun it.
•	Modeling (Using many ARCH, GARCH model, GARCH-M model, so on according to the article coooool ) and compare and choose the best.
•	Out of sample test
•	Conclusion
NB : - Coooooooool is the article to replicate a part.
        - The word paper is what I have done until now ( but in french).
        - The word code is the code R programming. You can copy and paste in your R logiciel.



Please, tell me if it is possible and how much it costs and how many days can you complete it?




```{r}
#rm(list = ls())
#Travail de session Finance 
#Importation des données 

base <- read.csv("base CSV.csv", header = TRUE, check.names = FALSE,sep=";", dec = ",")

base <- base[-2497:-5323,]

#Calucle des Spreads

rr <-100*diff(log(base$SP500_HYB))
rf <- 100*diff(log(base$SP_T_Bond))
CS= rr-rf

dCS= diff(CS)


#Graphe des rendements et de la valeur absolue des rendements

par(mfrow=c(3,2))

plot(ts(rr[1:2496],frequency = 252, start = 2010), xlab="",ylab="", type = "l", col = "blue", main = "S&P500 HYB return")
plot(ts(rf[1:2496],frequency = 252, start = 2010),xlab="",ylab="",type = "l", col = "red", main = "S&P Treasury Bond Return")
plot(ts(CS[1:2496],frequency = 252, start = 2010), xlab="",ylab="", type = "l", col = "green", main = "Credit Spread")
plot(ts(dCS[1:2496],frequency = 252, start = 2010), xlab="",ylab="", type = "l", col = "green", main = "variation du Credit Spread")


#Fonction permettant de calculer les statistiques descriptives des rendements
CS<-as.numeric(CS)
fct <- function(y){
  TT <- length(y)
  mm <- mean(y)
  vv <- sum((y-mm)^2)/TT
  ss <- sqrt(vv)
  z <- (y-mm)/sqrt(vv)
  Sk <- mean(z^3)  
  Ku <- mean(z^4)
  min<- min(y)
  max<-max(y)
  return(list(mean=mm,variance=vv,Etype = ss, skewness=Sk,kurtosis=Ku, Minimum=min , Maximum=max ))
}


#Statistiques descriptives
fct(CS)
fct(dCS)

# Test de normalité
# Histogramme
h <- hist(dCS, breaks=50, main="Histogram with Normal Curve", xlab="variation de Crédit Spread")


xfit <-seq(min(dCS),max(dCS),length=40) 
yfit<-dnorm(xfit,mean=mean(dCS),sd=sd(dCS)) 
yfit <- yfit*diff(h$mids[1:2])*length(dCS) 
lines(xfit, yfit, col="blue", lwd=2)




#QQ norm et QQ plot 

qqnorm(dCS); qqline(dCS)




```


```{r}


#Test de Jacques Berra 
library(tseries)
jarque.bera.test(dCS)

# Autocorrélation structure
#figure()
par(mfrow=c(2,2), mar=c(5,5,5,5))

# max lags for autocorrelation of returns and returns squared
mlag  <- 20

t <- seq(length(CS))
plot(t, y, type="l",
     main="(a) CS",
     xlab="t",
     ylab=expression(y[t]),
     bty="l")

plot(t, y^2, type="l",
     main="(b) dCS",
     xlab="t",
     ylab=expression(y[t]^2),
     bty="l")

acf(y, lag.max=mlag, plot=TRUE,
    main="(c) ACF Credit Spread",
    xlab="t",
    ylab=expression(acf(y[t])),
    bty="l")

acf(y^2, lag.max=mlag, plot=TRUE,
    main="(d) ACF dCS",
    xlab="t",
    ylab=expression(acf(y[t]^2)),
    bty="l")


figure()
xi <- seq(-6, 6, 0.1)
f <- bkde(y, range.x=c(-6, 6))
ft <- dnorm(xi, 0, 1)

plot(xi, ft, type="l", col="blue",
     xlab="y",
     lty=3,
     ylab=expression(f(y)),
     xlim = c(-6, 6),
     ylim=c(0, 0.6),      
     bty="l")
lines(f, col="red")


#Stationnarité du Credit Spread
#Cointégration




```

